---
title: "HUDK4051: Social Network Analysis"
author: "Charles Lang"
date: "1/26/2018"
output: html_document
---

In this assignment you will be generating and analyzing three social networks (also known as graphs or sociograms) based on three different measures. You will be using data from:

Representing Classroom Social Structure. Melbourne: Victoria Institute of
Secondary Education, M. Vickers and S. Chan, (1981)

Available from the Index of Complex Networks ([ICON](https://icon.colorado.edu/#!/))

The data were collected by Vickers & Chan from 29 seventh grade students in a school in Victoria, Australia. Students were asked to nominate their classmates on a number of relations including the following three "layers":  

1. Who do you get on with in the class?  
2. Who are your best friends in the class?  
3. Who would you prefer to work with?  

You have a data set for each of these questions, please complete the following tasks.

## Data Wrangling

Manipulate each of the data sets so that it is suitable for building a social network using iGraph.

```{r}
library("dplyr")
D1 <- read.csv("get.on.with.csv")
D2 <- read.csv("best.friends.csv")
D3 <- read.csv("work.with.csv")
nodes1 <- distinct(select(D1, from, gender.from))
links1 <- select(D1, from, to)

nodes2 <- distinct(select(D2, from, gender.from))
links2 <- select(D2, from, to)

nodes3 <- distinct(select(D3, from, gender.from))
links3 <- select(D3, from, to)
```

## Visualize the Networks

Create a graph for each of the data sets, are the graphs directed or undirected? Visualize each of the graphs you have created and color the nodes according to gender. Save pdfs of your graphs in this directory for upload to Github.
**I made all 3 graphs directed. 

```{r}
###QUESTIONS###
# Is it necessary to make the graphs more readable? Is the default the optimal layout of actors?? According to what?
# Can we convert the get.on.with dataframe into matrix? since it seems it does not matter if it is directed or not.

library("igraph")

# Q1 graph #
net1 <- graph_from_data_frame(d=links1, vertices=nodes1, directed=TRUE)
class(net1)
net1

as_data_frame(net1, what = "vertices")# Check what construct the graph
as_data_frame(net1, what = "edges")

V(net1)$color = V(net1)$gender.from # Assign the "gender" attribute as the vertex color
V(net1)$color = gsub("female","pink",V(net1)$color) #Females will be pink
V(net1)$color = gsub("male","light blue",V(net1)$color) #Males will be light blue

pdf("get.on.with.pdf")
plot(net1 <- simplify(net1, remove.multiple = TRUE),
     edge.arrow.size=.3,
     vertex.label.color="black")
dev.off()

# Q2 graph #
net2 <- graph_from_data_frame(d=links2, vertices=nodes2, directed=TRUE)
class(net2)
net2

V(net2)$color = V(net2)$gender.from 
V(net2)$color = gsub("female","pink",V(net2)$color) 
V(net2)$color = gsub("male","light blue",V(net2)$color) 

pdf("best.friend.pdf")
plot(net2 <- simplify(net2, remove.multiple = TRUE),
     edge.arrow.size=.3,
     vertex.label.color="black")
dev.off()

# Q3 graph #
net3 <- graph_from_data_frame(d=links3, vertices=nodes3, directed=TRUE)
class(net3)
net3

V(net3)$color = V(net3)$gender.from 
V(net3)$color = gsub("female","pink",V(net3)$color) 
V(net3)$color = gsub("male","light blue",V(net3)$color) 

pdf("work.with.pdf")
plot(net3 <- simplify(net3, remove.multiple = TRUE),
     edge.arrow.size=.3,
     vertex.label.color="black")
dev.off()


###COMMENTS###
# Yay~~ I finally figured out how to change attributes according to other column in the dataframe.
# ~~~
```


## Centrality Measures

Who in the class has the highest degree centrality for each measure?
```{r}
degree(net1, mode = "in")
degree(net1, mode = "out")
degree(net1, mode = "all")
power_centrality(net1, nodes = V(net1), loops = FALSE, exponent = 0.5,
  rescale = FALSE, sparse = TRUE)
power_centrality(net1, nodes = V(net1), loops = FALSE, exponent = -0.5,
  rescale = FALSE, sparse = TRUE)
```

Does **degree centrality** mean the same thing for each of your networks? Does it make sense for each of your networks?

Who in the class has the highest closeness centrality?

```{r}
closeness(net1, mode="all", weights=NA)
eigen_centrality(net1, directed=T, weights=NA)
centr_eigen(net1, directed=T, normalized=T)
```
```{r}
betweenness(net1, directed=T, weights=NA)
centr_betw(net1, directed=T, normalized=T)
```

How does **betweeness centrality** differ from degree centrality? Is one more useful than the other? Does their utility differ between your three networks?

## Simple structures

Count the number of dyads and the number and type of triads using the following commands.
```{r}
dyad_census()
```
[Documentation](http://igraph.org/r/doc/dyad_census.html)

```{r}
triad_census()
```
[Documentation](http://igraph.org/r/doc/triad_census.html)

Do these metrics tell you anything about the networks? If so what?

## Cliques

Answer the following questions using the [clique functions](http://igraph.org/r/doc/cliques.html)

What is the size of the largest clique(s) in each of the three networks?

```{r}

```

Which nodes/vertices are in the largest cliques for the three networks? Is there much overlap?

```{r}

```

How many **maximal cliques** are there in each of the networks?

```{r}

```

## Components & Cutpoints

Find the cutpoints (articulation points) for each of the three networks you generated. What does this tell you about the graphs? Does what you find match a visual exploration of the networks?

## Putting it all together

Write a narrative description of the social ties among members of this 7th grade class using the network, centrality and structural metrics you have developed. Can you provide any recommendations to the teacher of this class based on your analysis? What other information would you want to know? Can you remeber being in seventh grade, does this refelct your experience?

```{r}